---
title: "coronavirus"
author: "Rachael McVicar"
date: "3/4/2020"
output: gitub_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Coronavirus

Here we analyze infection data for the 2019 novel Coronavirus COVID-19 (2019-nCoV) epidemic. The raw data is pulled from the Johns Hopkins University Center for Systems Science and Engineering (JHU CCSE) Coronavirus repository.

A CSV file is available here https://github.com/RamiKrispin/coronavirus-csv


```{r}
url <- "https://tinyurl.com/COVID-2019"
virus <- read.csv(url)

tail(virus)
```

> Q1. How mant total infected cases are there around the world?

```{r}
total_cases<- sum(virus$cases)
total_cases
```
144,233 cases around the world as of 3/4/2020 1:30pm
149,549 cases around the world as of 3/5/2020 4:05pm


> Q2. How many deaths linked to infected cases have there been?

Let's have a look at the *$type* column

```{r}
inds<- virus$type == "death"
death_cases<- sum(virus[inds, "cases"])
death_cases
```
3,254 deaths linked to total cases as of 3/5/2020 4:09pm


> Q3. What is the overall death rate?

percent death is...
```{r}
round(death_cases/total_cases * 100, 2)
```
2.18% of total COVID19 cases result in death



> Q4. What is the death rate in "Mainland China"?

if then statement?
```{r}
China.cases.only <- subset(virus, Country.Region == "Mainland China", select = TRUE)
summary(China.cases.only)
```
3/5/2020 4:36pm
confirmed:896 
death    :135 
recovered:902 
All in Mainland China


Okay so I have all the data, as seen in my summary(China.cases.only) command
but I want to take the "confirmed", "death", "recovered" and add them together..
```{r}
aggregate(cases ~ type, China.cases.only, sum)
total.cases.China<- aggregate(cases ~ type, China.cases.only, sum)
deaths.in.China<- subset(China.cases.only, type=="death", select= TRUE) #this number is legit
```
These numbers look bigger than I thought they would for China..
I think this gives me the 133,207 number I was originally getting.. why?
I don't know, lets just run with it:/



dude, I DONT GET IT, ugggg

> Q5a. What is the death rate in Italy, Iran, and the US?

Let's try starting fresh with the US then.. :/

```{r}
US.cases.only <- subset(virus, Country.Region == "US", select = TRUE)
summary(US.cases.only)
```
woot yay! so it worked, and 81 cases 
sooooo what type of data is "US.cases.only"
dataframe? how can I manipulate it? It has the answers, but how to I get them and knit them together into information I want to use? AHHH, cool, we're cool, okay let's breath ... :)

```{r}
plot(US.cases.only)
#nope, I want to see what I just made
head(US.cases.only)
#better
```

I want to add/sum the total number of cases in the US
```{r}
sum(US.cases.only$cases)
US.total.cases<- sum(US.cases.only$cases)
```
Did I do it??/ 172 seem high:/ whatever
I think there is supposed to be only 81 cases...

```{r}
inds<- US.cases.only$type == "death"
US.death.cases<- sum(US.cases.only[inds, "cases"])
US.death.cases
```
THAT NUMBER IS LEGIT!!!

```{r}
round(US.death.cases/US.total.cases * 100, 2)
```
YAAAAASSSSSS I F-ing did it!!! (sort of, I trust my "US.death.cases" value, but not my "US.total.cases" value :b  )

> Q5b. What is the death rate in Italy, Iran, and the US?

```{r}
Italy.cases.only <- subset(virus, Country.Region == "Italy", select = TRUE)
summary(Italy.cases.only)
```

type   
 confirmed:16  
 death    :14  
 recovered:11
Total sum: 41

total looks like 41 cases... wait so why is Italy reacting so extremely with the upcoming tourism? flights?
anyways, write the code, I should get that 41 number for total COVID19 cases in Italy
```{r}
sum(Italy.cases.only$cases)
Italy.cases.only
```
wrong... why?
Ohhhhhh my gosh, is this code not accounting for cases from one day to the next??
That would explain the over saturated number I've been getting

maybe   #US.total.cases<- sum(US.cases.only$cases, type== "confirmed" "death" "recovered", select= TRUE)
so that's a no

maybe     #sum(Italy.cases.only$type) 
nope

I could cheat a little:) I noticed there were 41 rows....
```{r}
Italy.cases.only
rowsum(Italy.cases.only)
?rowsum
```

I know I'm so close! Why can't I sum the rows?? I even used the R help page and google and I don't get it. I'm super close I know it.
