---
title: "coronavirus"
author: "Rachael McVicar"
date: "3/4/2020"
output: gitub_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Coronavirus

Here we analyze infection data for the 2019 novel Coronavirus COVID-19 (2019-nCoV) epidemic. The raw data is pulled from the Johns Hopkins University Center for Systems Science and Engineering (JHU CCSE) Coronavirus repository.

A CSV file is available here https://github.com/RamiKrispin/coronavirus-csv


```{r}
url <- "https://tinyurl.com/COVID-2019"
virus <- read.csv(url)

tail(virus)
```

> Q1. How mant total infected cases are there around the world?

```{r}
total_cases<- sum(virus$cases)
total_cases
```
144,233 cases around the world as of 3/4/2020

> Q2. How many deaths linked to infected cases have there been?


Let's have a look at the *$type* column

```{r}
inds<- virus$type == "death"
death_cases<- sum(virus[inds, "cases"])
```

> Q3. What is the overall death rate?

percent death is...
```{r}
round(death_cases/total_cases * 100, 2)
```



> Q4. What is the death rate in "Mainland China"?

```{r}
total_cases_China <- virus$Country.Region == "Mainland China"
head(total_cases_China)
plot(total_cases_China, "date" , "cases")
```
if then statement?

> Q5. What is the death rate in Italy, Iran, and the US?


