---
title: "CoronaVirus HW take 2"
output: github_document
---

---
title: "coronavirus"
author: "Rachael McVicar"
date: "3/4/2020"
output: gitub_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Coronavirus

Here we analyze infection data for the 2019 novel Coronavirus COVID-19 (2019-nCoV) epidemic. The raw data is pulled from the Johns Hopkins University Center for Systems Science and Engineering (JHU CCSE) Coronavirus repository.

A CSV file is available here https://github.com/RamiKrispin/coronavirus-csv


```{r}
url <- "https://tinyurl.com/COVID-2019"
virus <- read.csv(url)

tail(virus)
```
6 rows and 7 columns

> Q1. How mant total infected cases are there around the world?

```{r}
total_cases<- sum(virus$cases)
total_cases
```
155,031 cases around the world as of 3/6/2020 11:30pm



> Q2. How many deaths linked to infected cases have there been?

Let's have a look at the *$type* column

```{r}
inds<- virus$type == "death"
death_cases<- sum(virus[inds, "cases"])
death_cases
```
3,348 deaths linked to total cases as of 3/6/2020 11:30pm


> Q3. What is the overall death rate?

percent death is...
```{r}
round(death_cases/total_cases * 100, 2)
```
2.16% of total COVID19 cases result in death



> Q4. What is the death rate in "Mainland China"?


```{r}
table.China.cases<- subset(virus, Country.Region == "Mainland China", select = TRUE)
total.China.cases<- sum(table.China.cases$cases)
```
cases: 135,675


```{r}
table.China.deaths<- subset(table.China.cases, type=="death", select= TRUE) 
total.China.deaths<- sum(table.China.deaths$cases)
```
deaths: 3,013


and for the moment of truth!
```{r}
round(total.China.deaths/total.China.cases * 100, 2)
```
2.22% death rate in China. It's horrible news, but figured the code out!



> Q5. What is the death rate in Italy, Iran, and the US?
> 5A) ITALY

```{r}
table.Italy.cases<- subset(virus, Country.Region == "Italy", select = TRUE)
sum(table.Italy.cases$cases)
total.Italy.cases<- sum(table.Italy.cases$cases)
```
cases: 4,420


```{r}
table.Italy.deaths<- subset(table.Italy.cases, type=="death", select= TRUE) 
sum(table.Italy.deaths$cases)
total.Italy.deaths<- sum(table.Italy.deaths$cases)
```
deaths: 148


```{r}
round(total.Italy.deaths/total.Italy.cases * 100, 2)
```
3.35% death rate in Italy

> 5B) IRAN

```{r}
table.Iran.cases<- subset(virus, Country.Region == "Iran", select = TRUE)
sum(table.Iran.cases$cases)
total.Iran.cases<- sum(table.Iran.cases$cases)
```
cases: 4,359


```{r}
table.Iran.deaths<- subset(table.Iran.cases, type=="death", select= TRUE) 
sum(table.Iran.deaths$cases)
total.Iran.deaths<- sum(table.Iran.deaths$cases)
```
deaths: 107


```{r}
round(total.Iran.deaths/total.Iran.cases * 100, 2)
```
2.45% death rate in Iran

> 5C) US

```{r}
table.US.cases<- subset(virus, Country.Region == "US", select = TRUE)
sum(table.US.cases$cases)
total.US.cases<- sum(table.US.cases$cases)
```
cases: 241


```{r}
table.US.deaths<- subset(table.US.cases, type=="death", select= TRUE) 
sum(table.US.deaths$cases)
total.US.deaths<- sum(table.US.deaths$cases)
```
deaths: 12


```{r}
round(total.US.deaths/total.US.cases * 100, 2)
```
4.98% death rate in US

