---
title: "Structure based drug design"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## 

Me: First, when we import the protein structure from PDB (it will be bound to a compound), we want to separate the protein structure from that molecule.

Barry: Here we download and clean up the HIV-Pr structure(PDB: 1HSG) from PDB. 
Make a separate set of "protein only" and "ligand only" files.

```{r}
library(bio3d)
file.name<- get.pdb("1HSG")
file.name
```

We'll use `read.pdb`, `atom.select()`, and write `write.pdb()` functions to make our separate "protein only" and "ligand only" file
```{r}
read.pdb("1HSG")
hiv<- read.pdb(file.name)
?atom.select
```

```{r}
hiv.protein.only<- atom.select(hiv, "protein", value=TRUE)
hiv.ligand.only<- atom.select(hiv, "ligand", value=TRUE)
```

```{r}
?write.pdb
write.pdb(hiv.protein.only, file="1HSG_protein.pdb")
write.pdb(hiv.ligand.only, file="1HSG_ligand.pdb")
```

The next step is to use AutoDockTools to setup protein docking input
Need hydrogens to calculate energies when docking, done through "AutoDockTools"
charge and atom-type is the difference between .pdbqt vs .pdb files (charge & type)

```{r}

res <- read.pdb("all.pdbqt", multi=TRUE)
write.pdb(res, "results.pdb")
```

```{r}
library(bio3d)
res <- read.pdb("all.pdbqt", multi= TRUE)
write.pdb(res, "results.pdb")
```

