---
title: 'Class10: MacineLearningProject_take2'
author: "Rachael McVicar"
date: "2/7/2020"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Get our input data

Our data for today come from the Wisconsin Breast Cancer Diagnostic Data Set

```{r}
wisc.df <- read.csv("WisconsinCancer.csv")
head(wisc.df)
```

```{r}
wisc.data <- as.matrix(wisc.df[,3:32])
head(wisc.data)
```

> Q. How many patients are there in this dataset?

```{r}
nrow(wisc.df)
```

> Q. How many cancer and non-cancer patients are there?

```{r}
table(wisc.df$diagnosis)
```

```{r}
sum(wisc.df$diagnosis == "M")
```

> Q. How many columns are "_mean" values

```{r}
colnames(wisc.df)
```

We can use the `grep()` function to see this

```{r}
grep("_mean", colnames(wisc.data), value=TRUE)
```

We can take the `length()` of this to find how many matches there are 
```{r}
length(grep("_mean", colnames(wisc.data)))
```

```{r}
#View(wisc.data)
```

## Enter Principal Component Analysis

First we need to check whether our input data should be scaled. 
Lets check the sd() and mean() of all our columns in `wisc.data` 

```{r}
round(apply(wisc.data, 2, sd), 2)
```

## after class break

```{r}
wisc.pr <- prcomp( wisc.data, scale=TRUE )
summary(wisc.pr)
```

```{r}
biplot(wisc.pr)
```

Biplot just doesn't cut it, time to look at this using PCA. First need to access the results within the `wisc.pr` object.
```{r}
attributes(wisc.pr)
```

We want the $x component to make our PCA plot!
```{r}
plot(wisc.pr$x[,1:2], col=wisc.df$diagnosis)
```


```{r}
PCA.wisc.pr<- wisc.pr$x[,1:3]
hclust.wisc.pr<- hclust(dist(PCA.wisc.pr))
#View(hclust.wisc.pr)
plot(hclust.wisc.pr)
```

I don't know where it is good to *cut* a tree like this...
```{r}
wisc.pr.hc<- hclust( dist(wisc.pr$x[,1:3]), method="ward.D2")
plot(wisc.pr.hc)
```

```{r}
grps <- cutree(wisc.pr.hc, k=2)
table(grps)
```

```{r}
table(grps, wisc.df$diagnosis)
```


```{r}
kmeans(wisc.data, centers = 2)
```

```{r}
plot(wisc.pr$x[,1], wisc.pr$x[,2], col=grps)
```


## one last hoorah
## Predicting Malignancy Of New samples

```{r}

url <- "https://tinyurl.com/new-samples-CSV"
new <- read.csv(url)
npc <- predict(wisc.pr, newdata=new)
plot(wisc.pr$x[,1:2])
points(npc[,1], npc[,2], col="blue", pch=16)
```

```{r}
plot(wisc.pr$x[,1], wisc.pr$x[,2], col=grps)
points(npc[,1], npc[,2], col="blue", pch=16, cex=3)
text(npc[,1], npc[,2], labels=c(1,2), col="white")
```

