---
title: 'Lecture 6: R functions'
author: "Rachael McVicar"
date: "1/24/2020"
output:
  word_document: default
  html_document: default
---
## Section 1: Improving analysis code by writing functions

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

let's insert a code chunk with the shortcut `Option-CMD-i`




```{r}
plot(1:5, col="blue", type="o")
```

```{r}
x<- (1:10)
x
```

## More on reading input files

We will use the read.table() function again

```{r}
read.table("test1.txt", header=TRUE, sep= ",")
```

```{r}
read.table("test2.txt", header=TRUE, sep="$")
```

```{r}
read.table("test3.txt")
```


### back after break 
### 'R' first function (coding puns woooooo)

This is an example function named add with input `x` and `y`

```{r}
add <- function(x, y=1) {
 # Sum the input x and y
 x + y
}
```

let's try using it


```{r}
add(x=c(1,6,2), 4)
```

#2nd function wooo
A 2nd function to re-scale data to lie between 0 and 1
```{r}
rescale <- function(x) {
 rng <-range(x)
 (x - rng[1]) / (rng[2] - rng[1])
}
```

Lets test this function

```{r}
rescale(c(1:10,30,100))
```

```{r}
rescale(c(1:10, NA))
```

```{r}
x<- c(1:10, NA)
rescale(c(1:10, NA))
rng <- (range(x, na.rm=TRUE))

```

Fix for missing values NAs

```{r}
rescale2<- function(x) {
rng <- (range(x, na.rm=TRUE))
 (x - rng[1]) / (rng[2] - rng[1])
}
```

```{r}
rescale2(c(1:10, NA))
```

Taking things a bit too far.... :b

```{r}
rescale3 <- function(x, na.rm=TRUE, plot=FALSE) {
 if(na.rm) {
 rng <-range(x, na.rm=na.rm)
 } else {
 rng <-range(x)
 }
 print("Hello")
 answer <- (x - rng[1]) / (rng[2] - rng[1])
 print("is it me you are looking for?")
 if(plot) {
 plot(answer, typ="b", lwd=4)
 }
 print("I can see it in ...")
}
```

```{r}
rescale3(x, plot=TRUE)
```

## Section 2: Writing and calling a function
#Working with the bio3d package
To use the functions from any package we have installed we use the `library()` function to load it.

```{r}
library(bio3d)
```

# Can you improve this analysis code?
```{r}
s1 <- read.pdb("4AKE") # kinase with drug
s2 <- read.pdb("1AKE") # kinase no drug
s3 <- read.pdb("1E4Y") # kinase with drug
s1.chainA <- trim.pdb(s1, chain="A", elety="CA")
s2.chainA <- trim.pdb(s2, chain="A", elety="CA")
s3.chainA <- trim.pdb(s3, chain="A", elety="CA")
s1.b <- s1.chainA$atom$b
s2.b <- s2.chainA$atom$b
s3.b <- s3.chainA$atom$b
plotb3(s1.b, sse=s1.chainA, typ="l", ylab="Bfactor")
plotb3(s2.b, sse=s2.chainA, typ="l", ylab="Bfactor")
plotb3(s3.b, sse=s3.chainA, typ="l", ylab="Bfactor")
```



```{r}
s1<- read.pdb("4AKE")
```

```{r}
class(s1)
```

```{r}
str(s1)
```

```{r}
aa321(s1$seqres)
```

Can we take some complicated real life code, simplify, and apply it to other real like protein structures
```{r}
plotb3(s1.b, sse=s1.chainA, typ="l", ylab="Bfactor")
points(s2.b, col="blue", typ="l", lwd=2)
points(s3.b, col="red", typ="l", lwd=3)
```

